
\section{Intro}
\frame{ \frametitle{Who? What? Why?}
\begin{itemize}

\item Use python to replace Grep Awk Sed Perl. Speed up your daily job.
\\

\item Roberto Polli - Solutions Architect @ par-tec.it. Loves writing in C,
Java and Python. Red Hat Certified Engineer and Virtualization
Administrator.
\\

\item Par-Tec – Proud sponsor of this talk ;) Contributes to various FLOSS and
provides expertise in IT Infrastructure \& Services and Business Intelligence
solutions + Vertical Applications for the financial market.

\end{itemize}
}


\begin{pyframe}{Requirements}
\begin{itemize}
\item Docker and docker-compose with python 2.7+ 

\item course code from github \\\\
\end{itemize}

\begin{pycode*}

  #git clone https://github.com/ioggstream/python-course
  #git clone https://github.com/ioggstream/python-course
  #cd python-for-sysadmin
  #docker-compose up course
  #firefox http://localhost:8888
\end{pycode*}

\begin{itemize}
\item first part: \pymodule{nose, psutil}
\item second part: \pymodule{scipy, numpy, matplotlib}
\item third part: \pymodule{ansible}
\item \pyoptional{optional/advanced content}
\end{itemize}
\end{pyframe}

\frame{ \frametitle{How}
\begin{itemize}
\item Get ready $before$ starting: code is \href{https://github.com/ioggstream/python-course/tree/master/python-for-sysadmin/README.md}{here on github}!

\item \emph{Use notebooks or type everything} but \code{\#comments} and \code{try/except}

\item \emph{Type fast} with tab-completion and copy-paste
% \emph{Type smart} with \code{\%edit testfile.py}!

\item Be curious: inspect and print returned variables

\item $Never^{*}$ close your notebooks or skip cells: you'll lose your precious variables

\end{itemize}

* (ok, sometimes you can).
}

\begin{pyframe}{References}
\begin{itemize}
\item irc.freenode.net\# python - The Python Community :D
\item Python Cookbook 3rd ed. O'Reilly - David Beazley and Brian K. Jones
\item Programming Python 4th ed. O'Reilly - Mark Lutz
\item Dive into Python3 2nd ed. Apress - Mark Pilgrim
\item nose.readthedocs.org
\item github.com/ioggstream/python-course
\end{itemize}
\end{pyframe}
