\section{Intro}
\frame{ \frametitle{Who? What? Why?}
\begin{itemize}

\item Use python to replace Grep Awk Sed Perl. Speed up your daily job.

\item Roberto Polli - Community Manager @ Babel.it. Loves writing in C,
Java and Python. Red Hat Certified Engineer and Virtualization
Administrator.

\item Babel – Proud sponsor of this talk ;) Delivers large mail
 infrastructures based on Open Source software for Italian ISP and
 PA\@. Contributes to various FLOSS.
\end{itemize}
}


\begin{pyframe}{Requirements}
\begin{itemize}
\item python 2.7+, ipython

\item course code from github \\\\
\code{ \#git clone https://github.com/ioggstream/python-course}

\item test your environment (eg. numpy, scipy, matplotlib) \\\\
\code{ \#nosetests -vs test\_prerequisites.py }

\item first part: \pymodule{nose, psutil}
\item second part: \pymodule{scipy, numpy, matplotlib}
\end{itemize}
\end{pyframe}

\frame{ \frametitle{How}
\begin{itemize}
\item Get ready $before$ starting: code is \href{https://github.com/ioggstream/python-course/tree/master/python-for-sysadmin/README}{here on github}!

\item \emph{Type everything} but \code{\#comments} and \code{try/except}

\item \emph{Type fast} with tab-completion and copy-paste
% \emph{Type smart} with \code{\%edit testfile.py}!

\item Be curious: inspect and print returned variables

\item $Never^{*}$ close your iPython session: you'll lose your precious variables

\end{itemize}

* (ok, sometimes you can).
}

\begin{pyframe}{References}
\begin{itemize}
\item irc.freenode.net\# python - The Python Community :D
\item Python Cookbook 3rd ed. O'Reilly - David Beazley and Brian K. Jones
\item Programming Python 4th ed. O'Reilly - Mark Lutz
\item Dive into Python3 2nd ed. Apress - Mark Pilgrim
\item nose.readthedocs.org
\item github.com/ioggstream/python-course
\end{itemize}
\end{pyframe}
